References

### 2017-07-03 cv/20sec/XieXiaolei.tex
Revised my CV.
Added GPA to the CV.
Applied to BNY Mellon.

\begin{minipage}{0.15\linewidth}
  Oct. 2014 - Sep. 2017
\end{minipage} \hfill
\begin{minipage}{0.85\linewidth}
  \begin{itemize}
  \item \underline{Ph.D. in Mathematical Statistics}
  \item Copenhagen University, Denmark
  \item Areas of research:
    \begin{itemize}
      \item {\bf Time series analysis}: ARIMA, GARCH, stochastic volatility
        models
      \item {\bf Asset allocation \& risk management}: Principle component
        analysis; optimization of investor utility functions; extreme
        value theory
      \item {\bf Numerical methods}: Importance sampling, numerical
        optimization, estimation of GARCH(p,q) tail indices
    \end{itemize}
  \end{itemize}
\end{minipage}

\vspace{3mm}

\begin{minipage}{0.15\linewidth}
  Sep. 2011 - June 2014
\end{minipage} \hfill
\begin{minipage}{0.85\linewidth}
  \begin{itemize}
  \item \underline{M.Sc. in Mathematical Physics}
  \item Lund University, Sweden
  \item Thesis project: Distribution of eigenvalues of large
    sample covariance matrices in the infinite dimensional limit with
    a focus on the influence of autocorrelations and heavy tails. The
    theoretical derivation is based on the {\it free probability
      theory} and is checked against {\it intraday tick-by-tick
      prices} of high-volume Swedish stocks.
  \item Course work:    
    \begin{itemize}
      \item Mathematical methods of Physics and Engineering
      \item Statistical mechanics, Quantum mechanics, General
        relativity
    \end{itemize}
  \end{itemize}
\end{minipage}
\vspace{3mm}

\begin{minipage}{0.15\linewidth}
  Sep. 2005 - June 2008
\end{minipage}\hfill
\begin{minipage}{0.85\linewidth}
  \begin{itemize}
  \item \underline{M.Sc.Computer Science and Engineering}
  \item Helsinki University of Technology
  \item {\it Major Subject:} Mobile Computing - Services and Security
  \item {\it Average grade:} 4.17/5.
  \end{itemize}
\end{minipage}
\vspace{3mm}

\begin{minipage}{0.15\linewidth}
  Sep. 2001 - June 2005
\end{minipage}\hfill
\begin{minipage}{0.85\linewidth}
  \begin{itemize}
  \item \underline{B.Sc.Computer Science and Engineering}
  \item Beijing Institute of Technology
  \end{itemize}
\end{minipage}

@@

\section{Papers in Finalization}
\begin{itemize}
\item {\bf Xie, X.}, Mikosch, T. and de Vries, C., 2017,
  {\it Tail-indices and scale parameters of returns series}

@@

\section{Papers in Finalization}
\begin{itemize}
\item {\bf Xie, X.} Collamore, J, 2017
  {\it An efficient estimator of the probability of very large losses posed by
    GARCH(p,q) processes}

  {\small
    We propose an efficient importance sampling estimator of the
    probability of excursion over high thresholds (causing large
    losses) by Multivariate Markov chains e.g. a GARCH(p,q) process or
    a multivariate GARCH process.
    Although stationary distributions of these processes are known
    to have power-law tails, precise evaluation of the tail
    probabilities is difficult because the exact distribution is
    unknown. Moreover, naive simulation methods lead to erractic
    estimates. Our importance sampling estimator presents a solution.
  }
\end{itemize}
%----------------------------------------------------------------------------------------
%	 AWARDS
%----------------------------------------------------------------------------------------

@@

  {\it C, C++, Linux}
\item {\it
    \href{http://www.goodmillsystems.com}{\tt Goodmillsystems,
      Helsinki}, Software Designer, May 2007 - Sep 2007}

>>>>

\begin{minipage}{0.15\linewidth}
  Oct. 2014 - Sep. 2017
\end{minipage} \hfill
\begin{minipage}{0.85\linewidth}
  {\small
  \begin{itemize}
  \item \underline{Ph.D. in Mathematical Statistics}
  \item Copenhagen University, Denmark
  \item Areas of research:
    \begin{itemize}
      \item {\bf Time series analysis}: ARIMA, GARCH, stochastic volatility
        models
      \item {\bf Asset allocation \& risk management}: Principle component
        analysis; optimization of investor utility functions; extreme
        value theory
      \item {\bf Numerical methods}: Importance sampling, numerical
        optimization, estimation of GARCH(p,q) tail indices
    \end{itemize}
  \end{itemize}
  }
\end{minipage}

\vspace{2mm}

\begin{minipage}{0.15\linewidth}
  Sep. 2011 - June 2014
\end{minipage} \hfill
\begin{minipage}{0.85\linewidth}
  {\small
  \begin{itemize}
  \item \underline{M.Sc. in Mathematical Physics}
  \item Lund University, Sweden
  \item Thesis project: Distribution of eigenvalues of large
    sample covariance matrices in the infinite dimensional limit with
    a focus on the influence of autocorrelations and heavy tails. The
    theoretical derivation is based on the {\it free probability
      theory} and is checked against {\it intraday tick-by-tick
      prices} of high-volume Swedish stocks.
  \item Course work:    
    \begin{itemize}
      \item Mathematical methods of Physics and Engineering
      \item Statistical mechanics, Quantum mechanics, General
        relativity
    \end{itemize}
  \item Average grade: 87/100
  \end{itemize}
  }
\end{minipage}
\vspace{2mm}

\begin{minipage}{0.15\linewidth}
  Sep. 2005 - June 2008
\end{minipage}\hfill
\begin{minipage}{0.85\linewidth}
  {\small
    \begin{itemize}
    \item \underline{M.Sc.Computer Science and Engineering}
    \item Helsinki University of Technology
    \item {\it Major Subject:} Mobile Computing - Services and Security
    \item Average grade: 4.17/5
    \end{itemize}
  }
\end{minipage}
\vspace{2mm}

\begin{minipage}{0.15\linewidth}
  Sep. 2001 - June 2005
\end{minipage}\hfill
\begin{minipage}{0.85\linewidth}
  {\small
  \begin{itemize}
  \item \underline{B.Sc.Computer Science and Engineering}
  \item Beijing Institute of Technology
  \item Average grade: 89/100
  \end{itemize}
  }
\end{minipage}

@@

\section{Papers under Review}
\begin{itemize}
\item {\bf Xie, X.}, Mikosch, T. and de Vries, C., 2017,
  {\it Tail-indices and scale parameters of returns series}

@@

\section{Papers under Review}
\begin{itemize}
\item {\bf Xie, X.} Collamore, J, 2017
  {\it An efficient estimator of the probability of very large losses posed by
    GARCH(p,q) processes}

  {\small
    We propose an efficient importance sampling estimator of the
    probability of excursion over high thresholds (causing large
    losses) by Multivariate Markov chains e.g. a GARCH(p,q) process or
    a multivariate GARCH process.
    Although stationary distributions of these processes are known
    to have power-law tails, precise evaluation of the tail
    probabilities is difficult because the exact distribution is
    unknown. Moreover, naive simulation methods lead to erratic
    estimates. Our importance sampling estimator presents a solution.
  }
\end{itemize}
%----------------------------------------------------------------------------------------
%	 AWARDS
%----------------------------------------------------------------------------------------

@@

  {\it C, C++, Linux}
\item {\it
    \href{http://www.goodmillsystems.com}{\tt Goodmill Systems,
      Helsinki}, Software Designer, May 2007 - Sep 2007}
